Fig2: Candidate genes

### 2020-05-03 analysis/figure-2.Rmd
?

>>>>

###  tissue specific expression

```{r}
head(allvsd)

tissuespecificity <- allvsd %>%
  mutate(tissue = sapply(strsplit(as.character(samples),'\\_'), "[", 3)) %>% 
  group_by(X1) %>%
  summarize(tissues = str_c(tissue, collapse = ", ")) %>%
  filter(tissues != "gon, hyp, pit") %>%
  group_by(tissues) %>%
  summarize(genes = str_c(X1, collapse = ", ")) %>% 
  mutate(n = str_count(genes, ",") + 1) %>% 
  arrange(desc(n))
tissuespecificity
